Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-08 paper/overview.tex
Add new BriefCASE workflow figure

\begin{figure*}
	\begin{center}
	  \includegraphics[width=\textwidth]{./figs/tool-arch.jpg}
  	\end{center}
	\caption{\brfcs\ integrated tool architecture with key components in the general workflow shown in green.}
	\label{fig:tool-arch}
\end{figure*}

@@

\oldjunk{
Showing that a component is properly implemented is accomplished
through formal synthesis from the code contract (bottom of
\figref{fig:tool-arch}).  This paper presents the Semantic Properties
of Language and Automata Theory (\splt) tool that generates
\emph{\ckml} code to implement the code contract.  \ckml\ is a
functional language that includes additional proofs and tools built
around it \cite{cakeml}.  The \ckml\ compiler itself is verified to
generate binary implementations that are equivalent in semantics to
the original input program.  That proof ensures that the resulting
binary exactly preserves the meaning of the original code contract and
assures that the component is faithfully implemented.
}

>>>>

\begin{figure*}
	\begin{center}
	  \includegraphics[width=\textwidth]{./figs/workflow.png}
  	\end{center}
	\caption{The general workflow for \brfcs.}
	\label{fig:tool-arch}
\end{figure*}

@@

\oldjunk{
Showing that a component is properly implemented is accomplished
through formal synthesis from the code contract (bottom of
\figref{fig:tool-arch}).  This paper presents the Semantic Properties
of Language and Automata Theory (\splt) tool that generates
\emph{\ckml} code to implement the code contract.  \ckml\ is a
functional language that includes additional proofs and tools built
around it.  The \ckml\ compiler itself is verified to
generate binary implementations that are equivalent in semantics to
the original input program.  That proof ensures that the resulting
binary exactly preserves the meaning of the original code contract and
assures that the component is faithfully implemented.
}
